\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-10 paper.qmd
Updated Figure 12

```{r}
#| fig-cap: "Assessing which of the 5 NLDR layouts on the two C-shaped clusters data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). Layout d is universally poor. Layouts a that show two close clusters are universally suboptimal. Layout a is the best choice."
#| label: fig-two_non_linear_diff_shaped_close_clusters-mse
#| fig-pos: H
#| out-width: 60%

>>>>

```{r}
#| fig-cap: "Assessing which of the 6 NLDR layouts on the two C-shaped clusters data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). Layout d is universally poor. Layouts a that show two close clusters are universally suboptimal. Layout a is the best choice."
#| label: fig-two_non_linear_diff_shaped_close_clusters-mse
#| fig-pos: H
#| out-width: 60%

### 2025-01-10 paper.tex
Updated Figure 7 title
Updated Figure 12

\caption{\label{fig-bins-two-curvy}Hexbin density plots of tSNE layout
of the two C-shaped clusters data, using three different bin inputs: (a)
\(b = 80 \text{ } (10, \text{ }8)\), (b)
\(b = 130 \text{ } (13, \text{ }10)\), and (c)
\(b = 391 \text{ } (23, \text{ }17)\). Color indicates standardized
counts, dark indicating high count and light indicates low count. At the
smallest bin size, the data structure is discontinuous, suggesting that
there are too many bins. Using the MSE of the model fit in
\(7\text{-}D\) helps decide on a useful choice of number of bins.}

@@

\caption{\label{fig-two_non_linear_diff_shaped_close_clusters-mse}Assessing
which of the 5 NLDR layouts on the two C-shaped clusters data is the
better representation using MSE for varying binwidth (\(a_1\)). Colour
used for the lines and points in the left plot and in the scatterplots
represents NLDR layout (a-e). Layout d is universally poor. Layouts a
that show two close clusters are universally suboptimal. Layout a is the
best choice.}

>>>>

\caption{\label{fig-bins-two-curvy}Hexbin density plots of tSNE layout
of the two C-shaped clusters data, using three different bin inputs: (a)
\(b = 255 \text{ } (15, \text{ }17)\), (b)
\(b = 598 \text{ } (23, \text{ }26)\), and (c)
\(b = 2544 \text{ } (48, \text{ }53)\). Color indicates standardized
counts, dark indicating high count and light indicates low count. At the
smallest bin size, the data structure is discontinuous, suggesting that
there are too many bins. Using the MSE of the model fit in
\(7\text{-}D\) helps decide on a useful choice of number of bins.}

@@

\caption{\label{fig-two_non_linear_diff_shaped_close_clusters-mse}Assessing
which of the 6 NLDR layouts on the two C-shaped clusters data is the
better representation using MSE for varying binwidth (\(a_1\)). Colour
used for the lines and points in the left plot and in the scatterplots
represents NLDR layout (a-e). Layout d is universally poor. Layouts a
that show two close clusters are universally suboptimal. Layout a is the
best choice.}
